Deep Learning

### 2015-01-12 deepreview.tex
fixed incorrect citation to deep MT papers

So far, most applications of deep learning use feed-forward neural
networks, but for tasks that involve sequential inputs it is often better
to use recurrent neural networks. These are given one element from an input % YB term-->element
sequence at each time step and their recurrent internal ``hidden'' state
depends on the whole history of the input sequence. Recurrent networks are
very good at predicting the next character in a string~\citep{Sutskever-et-al-ICML2011} or
the next word in a sequence~\citep{Mikolov-et-al-NIPS2013} but they can also be used for
more complex tasks.  After reading an English sentence one word at a time,
for example, an English``encoder'' network can be trained so that the final
state vector of its hidden neurons is a good representation of the thought
expressed by the sentence.  This thought vector can then be used as the
initial hidden state of a trained French ``decoder'' network which outputs
a probability distribution for the first word of the French translation. If
a particular first word is chosen (e.g., according to that probability)
and provided as input to the decoder
network it will then output a probability distribution for the second word
of the translation and so on until a full stop is 
chosen~\citep{Vinyals-et-al-arxiv2014,Bahdanau-et-al-arxiv2014}. 
%YB added a clarification
Overall, this process generates sequences of French words according to
a probability distribution that depends on the English sentence.

>>>>

So far, most applications of deep learning use feed-forward neural
networks, but for tasks that involve sequential inputs it is often better
to use recurrent neural networks. These are given one element from an input % YB term-->element
sequence at each time step and their recurrent internal ``hidden'' state
depends on the whole history of the input sequence. Recurrent networks are
very good at predicting the next character in a string~\citep{Sutskever-et-al-ICML2011} or
the next word in a sequence~\citep{Mikolov-et-al-NIPS2013} but they can also be used for
more complex tasks.  After reading an English sentence one word at a time,
for example, an English``encoder'' network can be trained so that the final
state vector of its hidden neurons is a good representation of the thought
expressed by the sentence.  This thought vector can then be used as the
initial hidden state (or as extra input) of a trained French ``decoder'' 
network which outputs
a probability distribution for the first word of the French translation. If
a particular first word is chosen (e.g., according to that probability)
and provided as input to the decoder
network it will then output a probability distribution for the second word
of the translation and so on until a full stop is 
chosen~\citep{Bahdanau-et-al-arxiv2014,Sutskever-et-al-NIPS2014}. 
Overall, this process generates sequences of French words according to
a probability distribution that depends on the English sentence.
